Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-04-06 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-front.tex
Small changes in abs

\begin{abstract} The necessary intervention of humans in interactive
evolutionary computational systems has inherent drawbacks arising from the
very nature of the algorithms, namely, the human fatigue caused by the
interaction, and the boredom arising when users evaluate a large number of
artifacts. To tackle these issues, in this paper we propose a human-centered
framework that can be used to  increase volunteer participation in C-IEC 
systems by using gamification techniques. A case study is
presented where the model is applied in the development of a collaborative
evolutionary interactive system.
\end{abstract}

>>>>

\begin{abstract} The necessary intervention of humans in interactive
evolutionary computational systems has inherent drawbacks arising from the
very nature of the algorithms, namely, the human fatigue caused by the
interaction and the boredom arising when users evaluate a large number of
artifacts. To tackle these issues, in this paper we propose a human-centered
framework that can be used to increase volunteer participation in collaborative interactive evolutionary computational (C-IEC)
systems by using gamification techniques. A case study is
presented where the model is applied in the development of a collaborative
evolutionary interactive system.
\end{abstract}
